Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-09 paper.tex
edited the calculation a little
added the proof of Theorem 2 and Lemma 6

\begin{algorithm}
\caption{Algorithm: Upper Bound}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number; g(n) to be a increasing function which we choose later;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm is less than $g(n)^{-1}$ and we haven’t pulled that arm in this round}
	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

@@

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
\label{rst:budget}
\end{theorem}

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2) + O(N \sum_{n=1}^{T}n^{\alpha})$ for $-1<\alpha<0$.
\label{rst:regret}
\end{theorem}

@@

\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Ng(n)$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}

@@

Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i_{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$. At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
\begin{itemize}
\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $\frac{1}{g(n)}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled. In this case, the probability that the $i_{th}$ different arm will be pulled is 1.  
\item There exists at least $\frac{1}{g(n)}$ proportion of agents who will choose an un-pulled arm as his/her myopic action. In this case, we know each type of agent shows up with probability at least $p$. Thus, the probability that the $i_{th}$ different arm will be pulled is at least $\frac{1}{g(n)}$.
\end{itemize}

Since $X_{i}$ follows a ``geometric distribution'' with success probability at least $\frac{1}{g(n)}$ at each time, we know 
\begin{align}
E[t_{n}-t_{n-1}]\leq Ng(n). \nonumber
\end{align}
\end{proof}

\begin{lemma}
The expected incentive payment at round $n$ is bounded above by \bccomment{How to bound this conditional expectation?}
\end{lemma}

\begin{proof}
Denote $\Delta=\sup_{\theta}\max_{i}\{\theta\cdot u_{B(\theta)}-\theta\cdot u_{i}\}$ to be the theoretical maximum payment with no noisy. We first consider the expected payment for arm $1$ in the $n_{th}$ round. Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$.

\begin{align}
&E[\max_{i}\theta_t\cdot u_{i,t}-\theta_t\cdot u_{1,t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}] \nonumber \\
\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}] \nonumber 
\end{align}

Denote $p_1=P_{\theta\sim F}(B(\theta)=1)$.

If in the $n_{th}$ round we have $g(n)^{-1}>p_1$:

If in the $n_{th}$ round we have $g(n)^{-1}<\frac{p}{2}$:
\begin{align}
E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}]  \nonumber 
\end{align}

@@

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $1/g(n)<p/2$, we do not need to incentivize any arms.

Denote 
\begin{align}
n_{1}=\max\bigg\{50, \frac{23.04\sigma^4}{\lambda\left(p^{-1}(\frac{p}{2})\right)^4},\min_{n}\{n:1/g(n)<\frac{p}{2}\}\bigg\}. \nonumber
\end{align}

@@

\begin{align}
&E[C(T)] \nonumber \\
= & \sum_{t=1}^{\infty}E[\mathbbm{1}\{\text{need to offer payment to an arm}\}] \nonumber \\
\leq &\sum_{n=1}^{\infty}\sum_{t=1}^{\infty}E[\mathbbm{1}\{t_{n-1}\leq t\leq t_{n}: \text{myopic action occurs regret for agents with } \nonumber \\
&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}(1/g(n))\}\}] \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}P(\text{myopic action occurs regret for agents with }\nonumber \\
&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}\left(\frac{p}{2}\right)\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+Nn_{1} \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Ng(n)+Nn_{1} \nonumber 
\end{align}

If we choose $g(n)=n$ and $\delta_{0}=p^{-1}(\frac{p}{2})$, then we have
\begin{align}
\frac{1}{n}<\frac{p}{2} \implies n\geq (\frac{2}{p})+1. \nonumber
\end{align}
We know the expected payment is bounded above by:
\begin{align}
E[C(T)] \leq 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
\end{align}

Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^2)$.\end{proof}

@@

\begin{proof}
For regret occurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRg(n)$.

@@

Thus, the cumulative expected regret occured up to time $T$ when we let the agent play myopically is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + E\left[\sum_{t=t_{n_{0}}}^{T}r_1(t)\right]+ E\left[\sum_{t=t_{n_{0}}}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Ng(n)+ \sum_{t=1}^{T}Mf(t)^2 \nonumber
\end{align}

The expected regret occurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus if we set $g(n)=n$, the cumulative regret at time $T$ is bounded above by
\begin{align}
&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
\end{align}

@@

For a fixed $T$, if we choose $f(n)=n^{-1/2+\frac{1}{2\log(T)}}$, we have
\begin{align}
&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{T} 24N^{2} Rmn\exp\left(-\frac{1.8n^{1/\log(T)}}{32 m^2\sigma^2}\right) + \left(\sum_{t=1}^{T} Mn^{-1}\right) \times T^{\frac{1}{\log(T)}} \nonumber \\
= & + e(\log(T) + 1)
\end{align}

@@

In this section, we consider a special case of our problem, in which the agent's preference distribution $F(\cdot)$ satisfies $S(\delta)=0$ for $\delta<\delta^{'}$. Under this assumption, we still have $O(N^2)$ budget bound, however we get a better regret bound. The proof is similar to the proof of Theorem~\ref{rst:regret}, but for $t$ large enough, $S(f(t))=0$. Thus,

@@

In our algorithm, we take ``pay what it takes'' strategy when we decided to incentivize the agent. However, as long as

>>>>

\begin{algorithm}
\caption{Algorithm: Upper Bound}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and we haven’t pulled that arm in this round}
	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

@@

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$.
\label{rst:budget}
\end{theorem}

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2\log(T))$.
\label{rst:regret}
\end{theorem}

@@

\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Nn$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}

@@

Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i_{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$. At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
\begin{itemize}
\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $n^{-1}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled. In this case, the probability that the $i_{th}$ different arm will be pulled is 1.  
\item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action. In this case, we know each type of agent shows up with probability at least $p$. Thus, the probability that the $i_{th}$ different arm will be pulled is at least $n^{-1}$.
\end{itemize}

Since $X_{i}$ follows a ``geometric distribution'' with success probability at least $n^{-1}$ at each time, we know 
\begin{align}
E[t_{n}-t_{n-1}]\leq Nn. \nonumber
\end{align}
\end{proof}

\begin{lemma}
For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + Nm \sqrt{\frac{2}{n\pi}}$. 
\end{lemma}

\begin{proof}
Denote $\Delta=\sup_{\theta}\max_{i}\{\theta\cdot u_{B(\theta)}-\theta\cdot u_{i}\}$ to be the theoretical maximum payment with no noisy. We consider the expected payment in the $n_{th}$ round. Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$.

\begin{align}
&E[c(t)] \nonumber \\
\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}1\{c(t)>0\}] \nonumber \\
\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}] \nonumber \\
\leq & \Delta + \sum_{j=1}^{m}E[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
\leq & \Delta + \sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
\leq & \Delta + Nm E[|\epsilon_{1,t}^{1}|] \nonumber \\
\leq & \Delta + Nm \sqrt{\frac{2}{n\pi}} \nonumber
\end{align}

@@

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}<p/2$, we do not need to incentivize any arms.

Denote 
\begin{align}
n_{1}=\max\bigg\{50, \frac{23.04\sigma^4}{\lambda\left(p^{-1}(\frac{p}{2})\right)^4},\min_{n}\{n:n^{-1}<\frac{p}{2}\}\bigg\}. \nonumber
\end{align}

@@

\begin{align}
&E[C(T)] \nonumber \\
= & \sum_{t=1}^{\infty}E[c(t)\mathbbm{1}\{\text{need to offer payment to an arm}\}] \nonumber \\
\leq &\sum_{n=1}^{\infty}\sum_{t=1}^{\infty}E[c(t)\mathbbm{1}\{t_{n-1}\leq t\leq t_{n}: \text{myopic action occurs regret for agents with } \nonumber \\
&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}(n^{-1})\}\}] \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\left(\Delta+Nm\sqrt{\frac{2}{n\pi}}\right)P(\text{myopic action occurs regret for agents with }\nonumber \\
&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}\left(\frac{p}{2}\right)\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Nn\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber 
\end{align}

Denote $\delta_{0}=p^{-1}(\frac{p}{2})$, then we have
\begin{align}
\frac{1}{n}<\frac{p}{2} \implies n\geq (\frac{2}{p})+1. \nonumber
\end{align}
Thus, $n_1=\max\{n_{0}, \frac{2}{p}+1\}$. We know the expected payment is bounded above by:
\begin{align}
E[C(T)] \leq 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right). \nonumber
\end{align}

Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^3)$.

Based on this analysis, we know the expected number of payments we need to make is less than
\begin{align}
&\sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Nn+Nn_{1} \nonumber \\
=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
\end{align}

which we will use in the proof of Theorem~\ref{rst:regret}.

@@

\begin{proof}
For regret occurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.

@@

Thus, the cumulative expected regret occured up to time $T$ when we let the agent play myopically is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{t=t_{n_{0}}}^{T}r_1(t)\right]+ E\left[\sum_{t=t_{n_{0}}}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber
\end{align}

The expected regret occurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus the cumulative regret at time $T$ is bounded above by
\begin{align}
&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
\end{align}

@@

If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8n}$, then
\begin{align}
&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{64m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 35.56 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
\leq &  12 N^2 m R  + 35.56 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
\end{align}

Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
\end{proof}

@@

In this section, we consider a special case of our problem, in which the agent's preference distribution $F(\cdot)$ satisfies $S(\delta)=0$ for $\delta<\delta^{'}$. The proof is similar to the proof of Theorem~\ref{rst:regret}, but for $t$ large enough, $S(f(t))=0$. In this case, with $O(N^3)$ payment budget, we can achieve $O(N^2)$ regret.

@@

In our algorithm, we take ``pay whatever it takes'' strategy when we decided to incentivize the agent. In our proof, the only time we used ''pay whatever it takes'' is in Lemma~\ref{round:length}. Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round. Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ will have at least $n^{-1}$ probability being pulled at time $t$, our results still hold true. We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$. Here is the revised algorithm which would work well in practice:

\begin{algorithm}
\caption{Algorithm: Upper Bound}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm $i$ is less than $n^{-1}$ and we haven’t pulled that arm $i$ in this round (if there are multiple such arms, pick one randomly)}
	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

The same proof would work and we can get the exact same results as ``pay whatever it takes'' strategy.
